KidsAIR wood stove grades and usage

### 2020-01-23 home_char_act_cleaning.Rmd
data cleaning

---
title: "KidsAIR home activity and characteristics cleaning"
author: "Ethan Walker"
date: "Started 13 Jan 2020, Updated 15 Jan 2020"
output: pdf_document
---

@@

wmt_home_char <- home_char_initial_wmt %>% 
  # rename variables
  mutate(home_winter_id = as.factor(HomeWinterID),
         residents_total = as.factor(Residents),
         residents_under5 = as.factor(Under5),
         residents_under18 = as.factor(Under18),
         residents_smoke = as.factor(Smoke),
         residents_smoke_inside = as.factor(SmokeInside),
         home_type = as.factor(HomeType),
         home_year_built = as.factor(YearHomeBuilt),
         home_sqft = as.numeric(SqFootage),
         home_floors = as.factor(NumFloors),
         home_bedrooms = as.factor(NumBedrooms),
         home_windows = as.factor(NumWindows),
         home_pets = as.factor(NumPets),
         home_furry = as.factor(NumFurryPets),
         primary_heat = as.factor(PrimaryHeat),
         secondary_heat = as.factor(SecondaryHeat),
         stove_model = as.character(WoodstoveModel),
         stove_age = as.factor(WoodstoveAge),
         stove_cert = as.factor(WoodstoveEPACert),
         chimney_clean = as.factor(ChimneyCleaned),
         home_damp = as.factor(Damp),
         home_mold = as.factor(Mold),
         home_fireplace = as.factor(ExistingFireplace),
         home_furnace = as.factor(ExistingFurnace),
         home_woodstove = as.factor(ExistingWoodstove),
         home_insert = as.factor(ExistingInsert),
         area = "WMT") %>% 
  select(home_winter_id, area, residents_total, residents_under5,
         residents_under18, residents_smoke, residents_smoke_inside,
         home_type, home_year_built, home_sqft, home_floors, home_bedrooms,
         home_windows, home_pets, home_furry, primary_heat,
         secondary_heat, stove_model, stove_age, stove_cert, chimney_clean,
         home_damp, home_mold, home_fireplace, home_furnace,
         home_woodstove, home_insert) %>% 
  ungroup() %>% 
  arrange(home_winter_id)

@@

nn_home_char <- home_char_initial_nn %>% 
  # rename variables
  mutate(home_winter_id = as.factor(HomeWinterID),
         residents_total = as.factor(Residents),
         residents_under5 = as.factor(Under5),
         residents_under18 = as.factor(Under18),
         residents_smoke = as.factor(Smoke),
         residents_smoke_inside = as.factor(SmokeInside),
         home_type = as.factor(HomeType),
         home_year_built = as.factor(YearHomeBuilt),
         home_sqft = as.numeric(SqFootage),
         home_floors = as.factor(NumFloors),
         home_bedrooms = as.factor(NumBedrooms),
         home_windows = as.factor(NumWindows),
         home_pets = as.factor(NumPets),
         home_furry = as.factor(NumFurryPets),
         primary_heat = as.factor(PrimaryHeat),
         secondary_heat = as.factor(SecondaryHeat),
         stove_model = as.character(WoodstoveModel),
         stove_age = as.factor(WoodstoveAge),
         stove_cert = as.factor(WoodstoveEPACert),
         chimney_clean = as.factor(ChimneyCleaned),
         home_damp = as.factor(Damp),
         home_mold = as.factor(Mold),
         home_fireplace = as.factor(ExistingFireplace),
         home_furnace = as.factor(ExistingFurnace),
         home_woodstove = as.factor(ExistingWoodstove),
         home_insert = as.factor(ExistingInsert),
         area = "NN") %>% 
  select(home_winter_id, area, residents_total, residents_under5,
         residents_under18, residents_smoke, residents_smoke_inside,
         home_type, home_year_built, home_sqft, home_floors, home_bedrooms,
         home_windows, home_pets, home_furry, primary_heat,
         secondary_heat, stove_model, stove_age, stove_cert, chimney_clean,
         home_damp, home_mold, home_fireplace, home_furnace,
         home_woodstove, home_insert) %>% 
  ungroup() %>% 
  arrange(home_winter_id)

@@

ak_home_char <- home_char_initial_ak %>% 
  # rename variables
  mutate(home_winter_id = as.factor(HomeWinterID),
         residents_total = as.factor(Residents),
         residents_under5 = as.factor(Under5),
         residents_under18 = as.factor(Under18),
         residents_smoke = as.factor(Smoke),
         residents_smoke_inside = as.factor(SmokeInside),
         home_type = as.factor(HomeType),
         home_year_built = as.factor(YearHomeBuilt),
         home_sqft = as.numeric(SqFootage),
         home_floors = as.factor(NumFloors),
         home_bedrooms = as.factor(NumBedrooms),
         home_windows = as.factor(NumWindows),
         home_pets = as.factor(NumPets),
         home_furry = as.factor(NumFurryPets),
         primary_heat = as.factor(PrimaryHeat),
         secondary_heat = as.factor(SecondaryHeat),
         stove_model = as.character(WoodstoveModel),
         stove_age = as.factor(WoodstoveAge),
         stove_cert = as.factor(WoodstoveEPACert),
         chimney_clean = as.factor(ChimneyCleaned),
         home_damp = as.factor(Damp),
         home_mold = as.factor(Mold),
         home_fireplace = as.factor(ExistingFireplace),
         home_furnace = as.factor(ExistingFurnace),
         home_woodstove = as.factor(ExistingWoodstove),
         home_insert = as.factor(ExistingInsert),
         area = "AK") %>% 
  select(home_winter_id, area, residents_total, residents_under5,
         residents_under18, residents_smoke, residents_smoke_inside,
         home_type, home_year_built, home_sqft, home_floors, home_bedrooms,
         home_windows, home_pets, home_furry, primary_heat,
         secondary_heat, stove_model, stove_age, stove_cert, chimney_clean,
         home_damp, home_mold, home_fireplace, home_furnace,
         home_woodstove, home_insert) %>% 
  ungroup() %>% 
  arrange(home_winter_id)

@@

home_char_clean <- kids_home_char %>% 
  left_join(kids_linked_ids, by = c("area", "home_winter_id"))

>>>>

---
title: "KidsAIR home activity and characteristics cleaning"
author: "Ethan Walker"
date: "Started 13 Jan 2020, Updated 23 Jan 2020"
output: pdf_document
---

@@

wmt_home_char <- home_char_initial_wmt %>% 
  # rename variables
  mutate(home_winter_id = as.factor(HomeWinterID),
         residents_total = as.numeric(Residents),
         residents_under5 = as.numeric(Under5),
         residents_under18 = as.numeric(Under18),
         residents_smoke = as.factor(Smoke),
         residents_smoke_inside = as.factor(SmokeInside),
         home_type = as.factor(HomeType),
         home_year_built = as.numeric(YearHomeBuilt),
         home_sqft = as.numeric(SqFootage),
         home_floors = as.numeric(NumFloors),
         home_bedrooms = as.numeric(NumBedrooms),
         home_windows = as.numeric(NumWindows),
         home_pets = as.numeric(NumPets),
         home_furry = as.numeric(NumFurryPets),
         primary_heat = as.factor(PrimaryHeat),
         secondary_heat = as.factor(SecondaryHeat),
         stove_model = as.character(WoodstoveModel),
         stove_age = as.factor(WoodstoveAge),
         stove_cert = as.factor(WoodstoveEPACert),
         chimney_clean = as.factor(ChimneyCleaned),
         home_damp = as.factor(Damp),
         home_mold = as.factor(Mold),
         home_fireplace = as.factor(ExistingFireplace),
         home_furnace = as.factor(ExistingFurnace),
         home_woodstove = as.factor(ExistingWoodstove),
         home_insert = as.factor(ExistingInsert),
         area = "WMT") %>% 
  select(home_winter_id, area, residents_total, residents_under5,
         residents_under18, residents_smoke, residents_smoke_inside,
         home_type, home_year_built, home_sqft, home_floors, home_bedrooms,
         home_windows, home_pets, home_furry, primary_heat,
         secondary_heat, stove_model, stove_age, stove_cert, chimney_clean,
         home_damp, home_mold, home_fireplace, home_furnace,
         home_woodstove, home_insert) %>% 
  ungroup() %>% 
  arrange(home_winter_id)

@@

nn_home_char <- home_char_initial_nn %>% 
  # rename variables
   mutate(home_winter_id = as.factor(HomeWinterID),
         residents_total = as.numeric(Residents),
         residents_under5 = as.numeric(Under5),
         residents_under18 = as.numeric(Under18),
         residents_smoke = as.factor(Smoke),
         residents_smoke_inside = as.factor(SmokeInside),
         home_type = as.factor(HomeType),
         home_year_built = as.numeric(YearHomeBuilt),
         home_sqft = as.numeric(SqFootage),
         home_floors = as.numeric(NumFloors),
         home_bedrooms = as.numeric(NumBedrooms),
         home_windows = as.numeric(NumWindows),
         home_pets = as.numeric(NumPets),
         home_furry = as.numeric(NumFurryPets),
         primary_heat = as.factor(PrimaryHeat),
         secondary_heat = as.factor(SecondaryHeat),
         stove_model = as.character(WoodstoveModel),
         stove_age = as.factor(WoodstoveAge),
         stove_cert = as.factor(WoodstoveEPACert),
         chimney_clean = as.factor(ChimneyCleaned),
         home_damp = as.factor(Damp),
         home_mold = as.factor(Mold),
         home_fireplace = as.factor(ExistingFireplace),
         home_furnace = as.factor(ExistingFurnace),
         home_woodstove = as.factor(ExistingWoodstove),
         home_insert = as.factor(ExistingInsert),
         area = "NN") %>% 
  select(home_winter_id, area, residents_total, residents_under5,
         residents_under18, residents_smoke, residents_smoke_inside,
         home_type, home_year_built, home_sqft, home_floors, home_bedrooms,
         home_windows, home_pets, home_furry, primary_heat,
         secondary_heat, stove_model, stove_age, stove_cert, chimney_clean,
         home_damp, home_mold, home_fireplace, home_furnace,
         home_woodstove, home_insert) %>% 
  ungroup() %>% 
  arrange(home_winter_id)

@@

ak_home_char <- home_char_initial_ak %>% 
  # rename variables
  mutate(home_winter_id = as.factor(HomeWinterID),
         residents_total = as.numeric(Residents),
         residents_under5 = as.numeric(Under5),
         residents_under18 = as.numeric(Under18),
         residents_smoke = as.factor(Smoke),
         residents_smoke_inside = as.factor(SmokeInside),
         home_type = as.factor(HomeType),
         home_year_built = as.numeric(YearHomeBuilt),
         home_sqft = as.numeric(SqFootage),
         home_floors = as.numeric(NumFloors),
         home_bedrooms = as.numeric(NumBedrooms),
         home_windows = as.numeric(NumWindows),
         home_pets = as.numeric(NumPets),
         home_furry = as.numeric(NumFurryPets),
         primary_heat = as.factor(PrimaryHeat),
         secondary_heat = as.factor(SecondaryHeat),
         stove_model = as.character(WoodstoveModel),
         stove_age = as.factor(WoodstoveAge),
         stove_cert = as.factor(WoodstoveEPACert),
         chimney_clean = as.factor(ChimneyCleaned),
         home_damp = as.factor(Damp),
         home_mold = as.factor(Mold),
         home_fireplace = as.factor(ExistingFireplace),
         home_furnace = as.factor(ExistingFurnace),
         home_woodstove = as.factor(ExistingWoodstove),
         home_insert = as.factor(ExistingInsert),
         area = "AK") %>% 
  select(home_winter_id, area, residents_total, residents_under5,
         residents_under18, residents_smoke, residents_smoke_inside,
         home_type, home_year_built, home_sqft, home_floors, home_bedrooms,
         home_windows, home_pets, home_furry, primary_heat,
         secondary_heat, stove_model, stove_age, stove_cert, chimney_clean,
         home_damp, home_mold, home_fireplace, home_furnace,
         home_woodstove, home_insert) %>% 
  ungroup() %>% 
  arrange(home_winter_id)

@@

home_char_clean <- kids_home_char %>% 
  left_join(kids_linked_ids, by = c("area", "home_winter_id")) %>% 
  # cleaning based on checking odd values with paper logs
  mutate(residents_under5 = if_else(residents_under5 == 10, 1, residents_under5)) %>% 
  replace_with_na(replace = list(home_year_built = 0)) %>% 
  replace_with_na(replace = list(home_floors = 0)) %>% 
  replace_with_na(replace = list(home_windows = 0)) %>% 
  replace_with_na(replace = list(residents_total = 0)) %>% 
  replace_with_na(replace = list(residents_under5 = 0)) %>% 
  replace_with_na(replace = list(residents_under18 = 0)) %>% 
  replace_with_na(replace = list(home_sqft = 0)) %>% 
  mutate(home_year_built = if_else(home_year_built == 15, 2002, home_year_built),
         home_year_built = if_else(home_year_built == 874, 1980, home_year_built)) %>% 
  replace_with_na(replace = list(home_year_built = 1400)) %>% 
  mutate(home_sqft = if_else(home_sqft == 14 & home == "CH102", 360, home_sqft),
         home_sqft = if_else(home_sqft == 14 & home == "CH107", 1152, home_sqft)) %>% 
  replace_with_na(replace = list(home_sqft = 12)) %>% 
  replace_with_na(replace = list(home_sqft = 14)) %>% 
  replace_with_na(replace = list(home_sqft = 20)) %>% 
  replace_with_na(replace = list(home_sqft = 24)) %>% 
  replace_with_na(replace = list(home_sqft = 90)) %>% 
  mutate(home_furry = if_else(home_furry == 4 & home == "WMA368", 1, home_furry),
         home_furry = if_else(home_furry == 10 & home == "WMA345", 14, home_furry),
         home_furry = if_else(home == "WMA309", 3, home_furry),
         home_pets = if_else(home == "WMA309", 3, home_pets),
         home_pets = if_else(home == "WMA437", 3, home_pets),
         home_furry = if_else(home == "WMA437", 3, home_furry)) %>% 
  replace_with_na(replace = list(home_furry = 14)) %>% 
  ungroup() %>% 
  arrange(area, home, winter_id)

### 2020-01-23 home_char_act_summary.Rmd
data cleaning

---
title: "Kids home characteristics/activity summary"
author: "Ethan Walker"
date: "Started 15 Jan 2020, Updated 15 Jan 2020"
output: pdf_document
---

@@

# Summary data for home characteristics
```{r}
# Summarize numeric vars
home_char_summary <- home_char_clean %>% 
  filter(winter_id == 1 | winter_id == 2) %>% 
  filter(home_sqft != 0) %>% 
  group_by(area, winter_id) %>% 
  summarize("N" = n(),
            "Mean Sqft" = mean(home_sqft, na.rm = TRUE), 
            "SD Sqft" = sd(home_sqft, na.rm = TRUE), 
            "Min Sqft" = min(home_sqft, na.rm = TRUE), 
            "Median Sqft" = median(home_sqft, na.rm = TRUE), 
            "Max Sqft" = max(home_sqft, na.rm = TRUE))
kable(home_char_summary, digits = 1, align = "c")

@@

home_plot <- data %>% 
  filter(winter_id == 1) %>% 
  filter(home_sqft != 0) %>%
  select(area, variable) %>% 
  rename(plot_var = variable) %>% 
  #na.exclude() %>% 
  ggplot() +
    geom_bar(aes(plot_var, fill = area)) +
    theme_minimal() +
    labs(title = variable) +
    theme(axis.text.x = element_text(size = 16, colour = "black", 
                                     angle = 40, vjust = 0.7, hjust = 0.7),
          axis.text.y = element_text(size = 16, colour = "black"),
          title = element_text(size = 18, colour = "black"),
          legend.text = element_text(size = 14, colour = "black"),
          legend.title = element_text(size = 16, colour = "black"),
          axis.title.y = element_blank(),
          axis.title.x = element_blank(),
          axis.line.x = element_line(colour = "black", size = 1.2), 
          axis.line.y = element_line(colour = "black", size = 1.2), 
          axis.ticks = element_blank(),
          panel.grid = element_blank()) +
    scale_fill_manual(values = jv_palette)
home_plot

@@

home_plot <- data %>% 
  filter(winter_id == 1) %>% 
  select(area, variable) %>% 
  rename(plot_var = variable) %>% 
  #na.exclude() %>% 
  ggplot() +
    geom_bar(aes(plot_var, fill = area)) +
    theme_minimal() +
    labs(title = variable) +
    theme(axis.text.x = element_text(size = 16, colour = "black", 
                                     angle = 40, vjust = 0.7, hjust = 0.7),
          axis.text.y = element_text(size = 16, colour = "black"),
          title = element_text(size = 18, colour = "black"),
          legend.text = element_text(size = 14, colour = "black"),
          legend.title = element_text(size = 16, colour = "black"),
          axis.title.y = element_blank(),
          axis.title.x = element_blank(),
          axis.line.x = element_line(colour = "black", size = 1.2), 
          axis.line.y = element_line(colour = "black", size = 1.2), 
          axis.ticks = element_blank(),
          panel.grid = element_blank()) +
    scale_fill_manual(values = jv_palette)
home_plot

>>>>

---
title: "Kids home characteristics/activity summary"
author: "Ethan Walker"
date: "Started 15 Jan 2020, Updated 23 Jan 2020"
output:
  pdf_document: default
  word_document: default
---

@@

# Summary data for home characteristics
```{r}
# Summarize numeric vars
home_char_summary <- home_char_clean %>% 
  #filter(winter_id == 1 | winter_id == 2) %>% 
  filter(winter_id == 1 & treatment == "Placebo") %>% 
  group_by(area) %>% 
  summarize("N" = n(),
            "Mean Sqft" = mean(home_sqft, na.rm = TRUE), 
            "SD Sqft" = sd(home_sqft, na.rm = TRUE), 
            "Min Sqft" = min(home_sqft, na.rm = TRUE), 
            "Median Sqft" = median(home_sqft, na.rm = TRUE), 
            "Max Sqft" = max(home_sqft, na.rm = TRUE))
kable(home_char_summary, digits = 1, align = "c")

@@

home_plot <- data %>% 
  filter(winter_id == 1 & treatment == "Placebo") %>% 
  select(area, variable) %>% 
  rename(plot_var = variable) %>% 
  #na.exclude() %>% 
  ggplot() +
    geom_bar(aes(plot_var, fill = area)) +
    theme_minimal() +
    labs(title = variable) +
    theme(axis.text.x = element_text(size = 16, colour = "black", 
                                     angle = 40, vjust = 0.7, hjust = 0.7),
          axis.text.y = element_text(size = 16, colour = "black"),
          title = element_text(size = 18, colour = "black"),
          legend.text = element_text(size = 14, colour = "black"),
          legend.title = element_text(size = 16, colour = "black"),
          axis.title.y = element_blank(),
          axis.title.x = element_blank(),
          axis.line.x = element_line(colour = "black", size = 1.2), 
          axis.line.y = element_line(colour = "black", size = 1.2), 
          axis.ticks = element_blank(),
          panel.grid = element_blank()) +
    scale_fill_manual(values = jv_palette)
home_plot

@@

home_plot <- data %>% 
  filter(winter_id == 1 & treatment == "Placebo") %>% 
  select(area, variable) %>% 
  rename(plot_var = variable) %>% 
  #na.exclude() %>% 
  ggplot() +
    geom_bar(aes(plot_var, fill = area)) +
    theme_minimal() +
    labs(title = variable) +
    theme(axis.text.x = element_text(size = 16, colour = "black", 
                                     angle = 40, vjust = 0.7, hjust = 0.7),
          axis.text.y = element_text(size = 16, colour = "black"),
          title = element_text(size = 18, colour = "black"),
          legend.text = element_text(size = 14, colour = "black"),
          legend.title = element_text(size = 16, colour = "black"),
          axis.title.y = element_blank(),
          axis.title.x = element_blank(),
          axis.line.x = element_line(colour = "black", size = 1.2), 
          axis.line.y = element_line(colour = "black", size = 1.2), 
          axis.ticks = element_blank(),
          panel.grid = element_blank()) +
    scale_fill_manual(values = jv_palette)
home_plot

### 2020-01-23 indoor_temp_rh_summary.Rmd
data cleaning

---
title: "Kids indoor temp/RH summary"
author: "Ethan Walker"
date: "Started 15 Jan 2020, Updated 16 Jan 2020"
output: pdf_document
---

@@

# Summary stats
```{r}
temp_rh_summary <- indoor_temp_rh_clean %>%
  group_by(area) %>% 
  summarize_if(is.numeric, list(mean = mean, sd = sd, min = min, 
                                med = median, max = max), na.rm = TRUE) %>% 
  select(-area) %>% 
  t() 
kable(temp_rh_summary, col.names = c("Alaska", "Navajo", "Montana"), 
      digits = 1, align = "c")
```

@@

boxplots_temp_rh <- data %>% 
  # change input to plot different temp/RH variable
  select(area, variable) %>% 
  rename(plot_var = variable) %>% 
  na.exclude() %>% 
  ggplot(aes(area, plot_var)) +
    geom_boxplot(aes(size = 1), lwd = 1.2, colour = "black", 
               fatten = 1, outlier.size = 1.5, width = 0.35) +
    stat_summary(fun.y=mean, geom="point", shape=17, size=3, color="red") +
    theme_minimal() +
    #ylim(0, 100) +
    #geom_hline(yintercept = 50, color = "red", size = 1.2) +
    #labs(y = "Max indoor RH (%)") +
    #labs(aes(x = "", y = paste("48-hour indoor PM "[2.5], " (", mu, g/m^3, ")"))) +
    theme(axis.text.x = element_text(size = 16, colour = "black"),
          axis.text.y = element_text(size = 16, colour = "black"),
          axis.title.y = element_blank(),
          axis.title.x = element_blank(),
          axis.line.x = element_line(colour = "black", size = 1.2), 
          axis.line.y = element_line(colour = "black", size = 1.2), 
          axis.ticks = element_blank())
boxplots_temp_rh

>>>>

---
title: "Kids indoor temp/RH summary"
author: "Ethan Walker"
date: "Started 15 Jan 2020, Updated 23 Jan 2020"
output: pdf_document
---

@@

# Summary stats
```{r}
temp_rh_summary <- indoor_temp_rh_clean %>%
  filter(winter_id == 1 & treatment == "Placebo") %>% 
  group_by(area) %>% 
  summarize_if(is.numeric, list(mean = mean, sd = sd, min = min, 
                                med = median, max = max), na.rm = TRUE) %>% 
  select(-area) %>% 
  t() 
kable(temp_rh_summary, col.names = c("Alaska", "Navajo", "Montana"), 
      digits = 1, align = "c")
```

@@

boxplots_temp_rh <- data %>% 
  filter(winter_id == 1 & treatment == "Placebo") %>% 
  select(area, variable) %>% 
  rename(plot_var = variable) %>% 
  na.exclude() %>% 
  ggplot(aes(area, plot_var)) +
    geom_boxplot(aes(size = 1), lwd = 1.2, colour = "black", 
               fatten = 1, outlier.size = 1.5, width = 0.35) +
    stat_summary(fun.y=mean, geom="point", shape=17, size=3, color="red") +
    theme_minimal() +
    theme(axis.text.x = element_text(size = 16, colour = "black"),
          axis.text.y = element_text(size = 16, colour = "black"),
          axis.title.y = element_blank(),
          axis.title.x = element_blank(),
          axis.line.x = element_line(colour = "black", size = 1.2), 
          axis.line.y = element_line(colour = "black", size = 1.2), 
          axis.ticks = element_blank())
boxplots_temp_rh

### 2020-01-23 moisture_summary.Rmd
data cleaning

---
title: "Kids Moisture Summary"
author: "Ethan Walker"
date: "Started 22 Nov 2019, Updated 14 Jan 2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

@@

# Summary stats
```{r}
summary_moisture <- moisture_clean %>% 
  group_by(area) %>% 
  summarize(mean(moisture_ave, na.rm = TRUE), sd(moisture_ave, na.rm = TRUE),
            median(moisture_ave, na.rm = TRUE),
            min(moisture_ave, na.rm = TRUE), max(moisture_ave, na.rm = TRUE)) %>% 
  t()
summary_moisture
```

# Boxplots
```{r, fig.height=6, fig.width=5}
boxplots_moisture <- moisture_clean %>% 
  select(area, moisture_ave) %>% 
  na.exclude() %>% 
  ggplot(aes(area, moisture_ave)) +
    geom_boxplot(aes(size = 1), lwd = 1.2, colour = "black", 
               fatten = 1, outlier.size = 1.5, width = 0.35) +
    stat_summary(fun.y=mean, geom="point", shape=17, size=3, color="red") +
    theme_minimal() +
    ylim(0, 50) +
    #geom_hline(yintercept = 50, color = "red", size = 1.2) +
    labs(y = "Mean moisture content (%)") +
    #labs(aes(x = "", y = paste("48-hour indoor PM "[2.5], " (", mu, g/m^3, ")"))) +
    theme(axis.text.x = element_text(size = 16, colour = "black"),
          axis.text.y = element_text(size = 16, colour = "black"),
          axis.title.y = element_text(size = 16,
                                      margin = margin(t = 0, r = 20, b = 0, l = 0)),
          axis.title.x = element_blank(),
          axis.line.x = element_line(colour = "black", size = 1.2), 
          axis.line.y = element_line(colour = "black", size = 1.2), 
          axis.ticks = element_blank())
boxplots_moisture
```

>>>>

---
title: "Kids Moisture Summary"
author: "Ethan Walker"
date: "Started 22 Nov 2019, Updated 23 Jan 2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, eval = TRUE, 
                      include = TRUE, warning = FALSE)
```

@@

# Moisture content summary stats
## Average of 3 measurements
```{r}
summary_moisture <- moisture_clean %>%
  filter(winter_id == 1 & treatment == "Placebo") %>% 
  group_by(area) %>% 
  summarize(mean = mean(moisture_ave, na.rm = TRUE), 
            SD = sd(moisture_ave, na.rm = TRUE),
            median = median(moisture_ave, na.rm = TRUE),
            min = min(moisture_ave, na.rm = TRUE), 
            max = max(moisture_ave, na.rm = TRUE)) %>%
  select(-area) %>% 
  t() 
kable(summary_moisture, col.names = c("Alaska", "Navajo", "Montana"), 
      digits = 1, align = "c")
```

# Was wood split?
```{r}
wood_split <- moisture_clean %>% 
  filter(winter_id == 1 & treatment == "Placebo") %>% 
  filter(!is.na(moisture_split)) %>% 
  group_by(area, moisture_split) %>% 
  summarise(n = n())
kable(wood_split, align = "c")
```

# Boxplots
```{r, fig.height=6, fig.width=5}
boxplots_moisture <- moisture_clean %>% 
  filter(winter_id == 1 & treatment == "Placebo") %>% 
  select(area, moisture_ave) %>% 
  na.exclude() %>% 
  ggplot(aes(area, moisture_ave)) +
    geom_boxplot(aes(size = 1), lwd = 1.2, colour = "black", 
               fatten = 1, outlier.size = 1.5, width = 0.35) +
    stat_summary(fun.y=mean, geom="point", shape=17, size=3, color="red") +
    theme_minimal() +
    ylim(0, 50) +
    #geom_hline(yintercept = 50, color = "red", size = 1.2) +
    labs(y = "Mean moisture content (%)") +
    #labs(aes(x = "", y = paste("48-hour indoor PM "[2.5], " (", mu, g/m^3, ")"))) +
    theme(axis.text.x = element_text(size = 16, colour = "black"),
          axis.text.y = element_text(size = 16, colour = "black"),
          axis.title.y = element_text(size = 16,
                                      margin = margin(t = 0, r = 20, b = 0, l = 0)),
          axis.title.x = element_blank(),
          axis.line.x = element_line(colour = "black", size = 1.2), 
          axis.line.y = element_line(colour = "black", size = 1.2), 
          axis.ticks = element_blank())
boxplots_moisture
```

### 2020-01-23 pm_summary.Rmd
data cleaning

---
title: "Kids PM Summary"
author: "Ethan Walker"
date: "Started 22 Nov 2019, Updated 15 Jan 2020"
output: pdf_document
---

@@

# Summary stats
```{r}
pm_summary <- pm_clean %>% 
  # group by: area, treatment, dtid, day_of_week, Sampling_day
  group_by(area) %>% 
  summarize("n" = n(),
            "Mean PM" = mean(pm, na.rm = TRUE), 
            "SD PM" = sd(pm, na.rm = TRUE),
            "Min PM" = min(pm, na.rm = TRUE), 
            "Median PM" = median(pm, na.rm = TRUE),
            "Max PM" = max(pm, na.rm = TRUE),
            "Mean Sample Days" = mean(pm_sample_interval, na.rm = TRUE),
            "Mean Sample Obs" = mean(pm_total_observations, na.rm = TRUE),
            "Mean % Daily Obs" = mean(percent_daily_obs_pm, na.rm = TRUE)) %>% 
  select(-area) %>% 
  t()

@@

# Boxplots for PM by study area
```{r, fig.height=6, fig.width=5}
boxplots_kids_pm <- pm_clean %>% 
  #filter(pm < 500) %>% 
  ggplot(aes(area, pm)) +
    geom_boxplot(aes(size = 1), lwd = 1.2, colour = "black", 
               fatten = 1, outlier.size = 1.5, width = 0.35) +
    stat_summary(fun.y=mean, geom="point", shape=17, size=3, color="red") +
    theme_minimal() +
    ylim(0, 100) +
    #geom_hline(yintercept = 50, color = "red", size = 1.2) +
    labs(y = expression(paste("PM"[2.5], " (", mu, g/m^3, ")"))) +
    #labs(aes(x = "", y = paste("48-hour indoor PM "[2.5], " (", mu, g/m^3, ")"))) +
    theme(axis.text.x = element_text(size = 16, colour = "black"),
          axis.text.y = element_text(size = 16, colour = "black"),
          axis.title.y = element_text(size = 16,
                                      margin = margin(t = 0, r = 20, b = 0, l = 0)),
          axis.title.x = element_blank(),
          axis.line.x = element_line(colour = "black", size = 1.2), 
          axis.line.y = element_line(colour = "black", size = 1.2), 
          axis.ticks = element_blank())
boxplots_kids_pm
```

>>>>

---
title: "Kids PM Summary"
author: "Ethan Walker"
date: "Started 22 Nov 2019, Updated 23 Jan 2020"
output: pdf_document
---

@@

# Summary stats
```{r}
pm_summary <- pm_clean %>% 
  # group by: area, treatment, dtid, day_of_week, Sampling_day
  filter(winter_id == 1 & treatment == "Placebo") %>% 
  filter(pm < 500) %>% 
  group_by(area) %>% 
  summarize("n" = n(),
            "Mean PM" = mean(pm, na.rm = TRUE), 
            "SD PM" = sd(pm, na.rm = TRUE),
            "Min PM" = min(pm, na.rm = TRUE), 
            "Median PM" = median(pm, na.rm = TRUE),
            "Max PM" = max(pm, na.rm = TRUE),
            "Mean Sample Days" = mean(pm_sample_interval, na.rm = TRUE),
            "Mean Sample Obs" = mean(pm_total_observations, na.rm = TRUE),
            "Mean % Daily Obs" = mean(percent_daily_obs_pm, na.rm = TRUE)) %>% 
  select(-area) %>% 
  t()

@@

# Boxplots for PM by study area
```{r, fig.height=6, fig.width=5}
boxplots_kids_pm <- pm_clean %>% 
  filter(winter_id == 1 & treatment == "Placebo") %>% 
  filter(pm < 500) %>% 
  ggplot(aes(area, pm)) +
    geom_boxplot(aes(size = 1), lwd = 1.2, colour = "black", 
               fatten = 1, outlier.size = 1.5, width = 0.35) +
    stat_summary(fun.y=mean, geom="point", shape=17, size=3, color="red") +
    theme_minimal() +
    ylim(0, 500) +
    #geom_hline(yintercept = 50, color = "red", size = 1.2) +
    labs(y = expression(paste("PM"[2.5], " (", mu, g/m^3, ")"))) +
    #labs(aes(x = "", y = paste("48-hour indoor PM "[2.5], " (", mu, g/m^3, ")"))) +
    theme(axis.text.x = element_text(size = 16, colour = "black"),
          axis.text.y = element_text(size = 16, colour = "black"),
          axis.title.y = element_text(size = 16,
                                      margin = margin(t = 0, r = 20, b = 0, l = 0)),
          axis.title.x = element_blank(),
          axis.line.x = element_line(colour = "black", size = 1.2), 
          axis.line.y = element_line(colour = "black", size = 1.2), 
          axis.ticks = element_blank())
boxplots_kids_pm
```

### 2020-01-23 stove_grade_usage_cleaning.Rmd
data cleaning

stove_use_clean <- kids_stove_use %>% 
  replace_with_na(replace = list(wood_cords = -999, wood_cords = 0)) %>% 
  mutate(wood_collect = factor(wood_collect,
                               levels = c("Less than 1 week",
                                          "Between 1 week and 1 month",
                                          "Between 1 month and 3 months",
                                          "Between 3 months and 6 months",
                                          "Between 6 months and 1 year",
                                          "More than 1 year"),
                               labels = c("< 1 week",
                                          "1 week to 1 mo",
                                          "1 mo to 3 mo",
                                          "3 mo to 6 mo",
                                          "6 mo to 1 year",
                                          "> 1 yr"))) %>% 
  left_join(kids_linked_ids, by = c("area", "home_winter_id"))

>>>>

stove_use_clean <- kids_stove_use %>% 
  replace_with_na(replace = list(wood_cords = -999)) %>%
  replace_with_na(replace = list(wood_cords = 0)) %>%
  mutate(wood_collect = factor(wood_collect,
                               levels = c("Less than 1 week",
                                          "Between 1 week and 1 month",
                                          "Between 1 month and 3 months",
                                          "Between 3 months and 6 months",
                                          "Between 6 months and 1 year",
                                          "More than 1 year"),
                               labels = c("< 1 week",
                                          "1 week to 1 mo",
                                          "1 mo to 3 mo",
                                          "3 mo to 6 mo",
                                          "6 mo to 1 year",
                                          "> 1 yr"))) %>% 
  left_join(kids_linked_ids, by = c("area", "home_winter_id"))
